Notes of Gravity and Entanglement

### 2016-09-06 G.R/G.R.tex
Initiating new fields: general relativity and quantum gravity.

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for the special character: differential "d".
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

\usepackage{xcolor} %For colourful math:http://tex.stackexchange.com/questions/21598/how-to-color-math-symbols

% To include PDF in higher version format.
\pdfoptionpdfminorversion=6

@@

\title{(Tentative) Calculating Green Function}
% TODO give it a better name.
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
    This is a note for reading the paper \cite{dissertation}, and for 
    understanding the code produced from that file.
}
\tableofcontents

\section{Chapter 1 - Introductions}
\label{sec:Chapter_1_-_Introductions}
This chapter is really a nice introduction to the current fields of 
mesoscopic physics. The writing is clear and it traces the develpment 
of this field. It gives me a lucid and holistic historical account of 
both the important discoveries and motives behind them. I should 
find those marked regions on pdf inside this part very useful.

\section{Chapter 2 - 2 Landauer-Büttiker formalism}
\label{sec:Chapter_2_-_2_Landauer-Buttiker_formalism}

This chapter introduces the Landauer-Büttiker formalism for calculating the
transport properties. The typical setup is illustrated below:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch2.setup_for_L-B_formalism}.png}
    \caption{Setup for the Landauer-Büttiker formalism}
    %\label{fig:}
\end{figure}

In that formalism, the currents following through the leads have the following
expression:
\begin{align}
    \label{eq:ch1.Landauer-Buttiker_formula}
    I_p = \frac{-e}{h} \sum_q \int T_{qp}(E)\left( f_p(E)-f_q(E) \right)\diff E
\end{align}
where $T_{pq}$ is the transmission coefficients for electrons to go from
lead $q$ to lead $p$. This formula can be simplified/linearized into:
\begin{align}
    I_p = \frac{e^2}{h}\sum_q T_{pq}(E_F)(V_p-V_q)
\end{align}
An obvious advantage of Landauer-Büttiker formalism is that it makes the
dependence of $I_p$ on experimental setup explicit in the formula.

This chapter continue to discuss some time reversal symmetry (TR) properties 
of this formula, centring/centering around the coefficient $T_{pq}$.
But I am perplexed by that he, while discussing TR, mentions the
magnetic field $B$ and formulae like:
\begin{align}
    T_{12}(+B)= T_{12}(-B)
\end{align}
\nomenclature{confusion: TR and $B$}{\nomrefpage}

\section{Chapter 3 - Tight-binding model}
\label{sec:Chapter_3_Tight-binding_model}

Here in this chapter the author presents the fundamental Hamiltonian of
the system under consideration.
\marginpar{
    Given the formula mentioned in previous chapter, the Hamiltonian
    presented here seemed seemingly extraneous. Read the introduction
    here in chapter 4 to understand the underlying logic.
}

The process to obtain the Hamiltonian is discretization the Hamiltonian
in continuous case, quite the reverse of the first few chapters of
A. Zee's QFT in a Nutshell. It should be noted that "a site may represent 
a region containing many atoms", although "this region should be small 
compared to physically relevant quantities such as the Fermi wavelength".

    \subsection{3.1 Spin-degenerate system}
    \label{sec:3.1_Spin-degenerate_system}
    Here the general Hamiltonian, using tight-binding model, is
    mentioned:
    \begin{align}
        H = &\sum_{n,m} 
            \left( t^x_{nm}\ket{n+1,m}\bra{n,m}
                +t^y_{nm}\ket{n,m+1}\bra{n,m}+h.c.\right)\nonumber\\
            &+\sum_{n,m} \epsilon_{nm}\ket{n,m}\bra{n,m}
    \end{align}

    The important thing is to determine the coefficient $t$.
    In the absence of magnetic field, $t$ is give by:
    \begin{align}
        t^x_{nm}=t^y_{nm}=-t=-\frac{\hbar^2}{2m^* a^2}
    \end{align}
    When magnetic field is present, we effect a so called Peierls
    substitution to get $t$.
    \marginpar{
        The author points to a paper, saying that it contains a
        "lucid discussion on the physics" of Peierls substitution.
        This might be something worth reading.
    }
    The result is, using Landau gauge in one dimensional under a
    homogeneous magnetic field.
    \begin{align}
        t^x_{nm} =& -t e^{i2\pi (m-1) \Phi/\Phi_0} \\
        t^y_{nm} =& -t
    \end{align}

    When the magnetic field is inhomogeneous, it is generally difficult
    to choose a gauge to calculate analytically. The author uses a
    very intuitive discretization process to approach this problem.
    The process is best illustrated by just the following picture:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.8\linewidth]{pics/{ch3.not-uniform_magnetic_field}.png}
        \caption{Not uniform magnetic field}
        \label{fig:ch3-uniform_magnetic_field.png}
    \end{figure}

    Therefore, the result is something like:
    \begin{align}
        t^x_{nm}=-t e^{i2\pi\sum_{m'<m}\Phi_{nm'}/\Phi_0}
    \end{align}
\printnomenclature
    \subsection{3.2 Including spin degrees of freedom}
    \label{sec:3.2_Including_spin_degrees_of_freedom}

    When the spin is taken into consideration, the formulation should
    be modified accordingly.

    If Zeeman/exchange splitting is considered, then:
    \begin{align}
        H_S = -\frac{1}{2}g^* \mu_B
            \sum_{nm}\ket{n,m}\bra{n,m}\otimes (B^{eff}_{nm}\cdot\sigma)
    \end{align}
    Not that the magnetic field strength here is only "effective".

    If Spin-orbit coupling is taken into consideration,
    \footnote{
        In my opinion, this is essentially all about Spin-Magnetic 
        field coupling, not just Spin-Orbital coupling.
    }
    the following Hamiltonian should be considered:
    \begin{align}
        H_{SO}= \lambda P\cdot (\bigtriangledown V \times \sigma)
        \label{eq:ch3.SO_coupling}
    \end{align}
    Here $P$ is the mechanical momentum operator, $\sigma$ is the
    three pauli spin matrix $(\sigma_x, \sigma_y, \sigma_z)$.

    The tight-binding version of this is too complicated to be presented
    here, it is on page 16, equation (3.20).

    One additional consideration is the Rashba spin-orbit coupling.
    This is the peculiar result of electrons trapped in a two
    dimensional surface. In the $Z$ direction, with $Z$ perpendicular
    to the 2 dimensional plane, the potential looks like something
    below, called a triangular potential:
    \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{pics/{ch3.rashba_spin-orbit_effect}.png}
        \caption{Conduction band at the interface of a semiconductor 
            heterostructure. Band bending creates a potential well 
            $V(z)$ confining the electrons to the XY plane. The asymmetry 
            of this well leads to Rashba spin-orbit coupling.}
        \label{fig:ch3-orbit_effect.png}
    \end{figure}
    It is pretty obvious, by equation \ref{eq:ch3.SO_coupling}, that
    this potential is going into our Hamiltonian.
    The result in tight-binding model is yet another complicated
    Hamiltonian, not to be presented here, numbered equation (3.23)
    on page 18.

\section{Chapter 4 - Green’s function formalism}
\label{sec:Chapter_4-Greens_function_formalism}

In this section we finally circled back to the Landauer-Büttiker
formalism. Here a breif summary of chapter 3 and 4 is opportune.
The purpose of chapter 3 and 4 as a whole, is to calculate the 
transmission coefficient $T_{qp}$ in equation
\ref{eq:ch1.Landauer-Buttiker_formula}. Here, chapter 3 establish the
Hamiltonian, and chapter 4 uses the Green function to calculate
transmission coefficient out of the Hamiltonian.

    \subsection{4.1 Green’s functions: The basics}
    \label{sec:4.1_Greens_functions_The_basics}

    The author takes the definition of Green's function as inverse
    of Hamiltonian, more specifically:
    \begin{align}
        [E-\hat{H}]\hat{G}(E) = 1
    \end{align}
    or, in the position-spin representation:
    \begin{align}
        [E-H(\vec{x})]G(\vec{x},\vec{x'},E)=\delta(\vec{x}-\vec{x'})
    \end{align}
    where $\vec{x}=(\vec{r},\sigma)$, containing in addition to the
    usual spatial part, the spin part.

    The physical meaning is also explained, although I learnt this
    better in A. Zee's QFT in a Nutshell. However, he notes that
    to disguish between the source and sink, i.e. to tell whether
    the Green's function calculated represents a wavefunction
    resulted from a unit excitation (the sink), or a source for such
    an excitation, we should incorporate boundary conditions. This is
    done by adding "an infinitesimal imaginary variable into the energy",
    "leading to the following definitions":
    \begin{align}
        G^{\pm}(\vec{x},\vec{x'},E)\equiv \lim_{\eta\to 0^{+}}
            G(\vec{x},\vec{x'},E\pm i\eta)
    \end{align}
    and $G^{\pm}$ satisfies:
    \begin{align}
        [E\pm i\eta - H(\vec{x})] G^{\pm}(\vec{x},\vec{x'},E)=
            \sigma(\vec{x}-\vec{x'})
    \end{align}
    The functions $G^+$ and $G^-$ are called respectively the
    \textbf{retarded and advanced Green's function}. The author
    mentions that, "when Fourier transforming the functions $G^\pm$ to
    the time domain using a closed contour integration in the complex 
    plane, they would correspond to causal and anticausal solutions".

    Though seemingly extraneous, the operator definition for above
    Green functions is also mentioned:
    \begin{align}
        \hat{G}^{\pm}(E)\equiv \lim_{\eta\to 0^+}
            \frac{1}{E\pm i\eta-\hat{H}}
    \end{align}
    \subsection{4.2 Transmission coefficients and the Green’s function}
    \label{sec:4.2_Transmission_coefficients_and_the_Greens_function}

    Here it is mentioned than the transmission coefficient is related
    Green's funciton in the following way:
    \begin{align}
        T_{pq} = \text{Tr}\left[\Gamma_p G_{pq}\Gamma_q G^{\dagger}_{pq}
                \right]
    \end{align}
    Here $G_{pq}$ is, to borrow the language of matrix mechanics,
    a submatrix of the Green's function. $\Gamma_p$ is a abbreviation
    for the following counting:
    \marginpar{I am not sure about this peculiar thing.}
    \begin{align}
        \label{eq:}
        \Gamma_p \equiv i(\sum_p-\sum^\dagger_p)
    \end{align}
    Here $\sum_p$ is named "self-energy of the lead", something I
    don't quite understand.
\section{Anchor}

\begin{thebibliography}{1}
    \bibitem{dissertation} 
        \href{https://sundoc.bibliothek.uni-halle.de/diss-online/07/07H039/prom.pdf}{Electronic Transport in Mesoscopic Systems}, 
        by von Georgo Metalidis. (Link found via Google)
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\usepackage{float}  % For H in figures
\usepackage{amsmath} % For math
\usepackage{amssymb}
\usepackage{mathrsfs}
% Followings are for the special character: differential "d".
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff[1]{\mathop{}\!\mathrm{d^#1}}
\numberwithin{equation}{subsection} % have the enumeration go to the subsection level.
                                    % See:https://en.wikibooks.org/wiki/LaTeX/Advanced_Mathematics
\usepackage{graphicx}   % need for figures
\usepackage{cite} % need for bibligraphy.
\usepackage[unicode]{hyperref}  % make every cite a link
\usepackage{CJKutf8} % For Chinese characters
\usepackage{fancyref} % For easy adding figure,equation etc in reference. Use \fref or \Fref instead of \ref
\usepackage{braket} %http://tex.stackexchange.com/questions/214728/braket-notation-in-latex

% Following is for theorems etc environments
% http://tex.stackexchange.com/questions/45817/theorem-definition-lemma-problem-numbering && https://en.wikibooks.org/wiki/LaTeX/Theorems
\usepackage{amsthm}
\newtheorem{defi}{Definition}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{ex}{Example}[section]

@@

\title{Notes for General Relativity}
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
    (None)
}
\tableofcontents
\section{The Principle of Relativity}
\label{sec:Principle_of_Relativity}
Landau's book \cite{landau} describes the speed of light, as a speed of the
maximum velocity of propagation of interaction. He perceives velocity as
describing the propagation of interaction.

In another aspect, I think that time does not exist. I perceive time as
a agent of the environmental effect, communicating information and 
coordinating movement between the system under consideration and its 
envrionment. Therefore, a single existance is eternal by nature. Perhaps 
before the universe originates, time is a meaningless concept. In my 
view, the light is the only reliable tool to serve function of
communication and coordination.

Fram either perspective, the speed of light is inherently constent.
However, from my view, it is not clear why this speed should be a maximum.

\subsection{Invariance of Interval}
\label{sec:Invariance of Interval}

The Landau's book\cite{landau}, introduces a

\begin{thebibliography}{1}
    \bibitem{landau} The Classical Theory of Fields
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

### 2016-09-06 Gravity and Entanglement/gravity_n_entanglement.tex
Initiating new fields: general relativity and quantum gravity.

\title{Notes for General Relativity}
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
    (None)
}
\tableofcontents
\section{The Principle of Relativity}
\label{sec:Principle_of_Relativity}
Landau's book \cite{landau} describes the speed of light, as a speed of the
maximum velocity of propagation of interaction. He perceives velocity as
describing the propagation of interaction.

In another aspect, I think that time does not exist. I perceive time as
a agent of the environmental effect, communicating information and 
coordinating movement between the system under consideration and its 
envrionment. Therefore, a single existance is eternal by nature. Perhaps 
before the universe originates, time is a meaningless concept. In my 
view, the light is the only reliable tool to serve function of
communication and coordination.

Fram either perspective, the speed of light is inherently constent.
However, from my view, it is not clear why this speed should be a maximum.

\subsection{Invariance of Interval}
\label{sec:Invariance of Interval}

The Landau's book\cite{landau}, introduces a

\begin{thebibliography}{1}
    \bibitem{landau} The Classical Theory of Fields
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

\title{Notes of Gravity and Entanglement}
\date{\today}
\author{Taper}

@@

\maketitle
\abstract{
This is my notes to \cite{utube_video}, a video lecture given by
professor Mark Van Raamsdonk. Also, it seems that this lecture is
unrelated to another paper of the same title, written by the same
author, on arXiv \cite{arxiv_paper}.
}
\tableofcontents

\section{Lecture}
\label{sec:Lecture}

We have reviewed ads/CFT, entanglement, some interesting connections
between entanglement structure of the CFT states, and the geometry
structure of the space time due to this state. If this is true, a natural
question is whether we can understand spacetime dynamics, i.e. gravitation,
from some physics related to entanglement.

Consider some CFT theory, assumning to satisfy the xxxxx (1'50) conjectur 
entanglement entropies are computed via:
xxxxx conjecture
2'17

\begin{align}
    S(A) = \frac{\text{Area}(\title{A})}{4G_N}
\end{align}

Some propertries that entanglement entropy must satisfy:
\begin{enumerate}
    \item sub-aditivity: $S(A and B)-S(A)-S(B) \geq 0$
\end{enumerate}
If there is some geometry due to the original states, will their entropy
statisfy the above constraints. Hence: \textbf{what do those constraints imply about
the spacetime geometry?}

Start with small perturbations to (?). 
\begin{thebibliography}{1}
    \bibitem{utube_video} Availalble on Youtube: \href{https://www.youtube.com/watch?v=ABJvMg5d9OY}{Mark Van Raamsdonk -Gravity and Entanglement}.
    \bibitem{arxiv_paper} \href{http://arxiv.org/abs/1609.00026v1}{arXiv:1609.00026v1}
\end{thebibliography}
\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
